Deep Probabilistic Models for Camera Geo-Calibration

### 2018-08-29 chapters/introduction/introduction.tex
before geo-calibration for feature learning

The first two contributions make our main approach. Our
algorithm feeds inputs (images, time and manual annotations) to
different constraint functions. Then
we fuse these constraint functions to simulate the joint distribution
over the complete geo-calibration parameters. We present the flowchart of
our approach in \figref{intro:architecture}.

Furthermore, we also explore to learning image features
and geo-calibrating cameras simultaneously.  We believe that camera
poses, geographic locations and image capture times are closely
related to image representations. 
Based on the belief that visual features which abstract the image
contents are the necessary for solving the geo-calibration tasks, we
designed neural networks to learn useful visual features by
geo-calibrating cameras. Our work provide new ways for automatic
feature learning.

@@

  \item \textbf{Constraint for Location and Orientation:}
  In our previous method, we present that our algorithm can estimate
  the discrete camera location. The predictions are only approximate
  due to the limitation of the algorithm. In this
  work, we propose a ground-to-aerial geo-calibration method that can
  further refine the prediction results and estimate the
  camera geo-orientation with overhead imagery.
%
  We first learn to deduce the semantic layout of the ground
  scene from the associated aerial image.
  Given a geographic location and orientation, we sample the aerial
  image, then compare its semantic layout of the ground scene
  with the semantic layout of the query image (ground image).
  We assign a score to that location and orientation by matching these
  two semantic layouts.
  We present the algorithm details in \chapref{crosstransf}.
  \newline

>>>>

The first two contributions make our main approach. Our
algorithm feeds inputs (images, time and manual annotations) to
different constraint functions. Then
we fuse these constraint functions to simulate the joint distribution
over the complete geo-calibration parameters. We present the flowchart of
our approach in \figref{intro:architecture}.
%
Furthermore, we also explore to learning image features
and geo-calibrating cameras simultaneously.  We believe that camera
poses, geographic locations and image capture times are closely
related to image representations. 
Based on the belief that visual features which abstract the image
contents are the necessary for solving the geo-calibration tasks, we
designed neural networks to learn useful visual features by
geo-calibrating cameras. Our work provide new ways for automatic
feature learning.

@@

  \item \textbf{Constraint for Location and Orientation:}
  In our previous method, we present that our algorithm can estimate
  the discrete camera location. The predictions are only approximate
  due to the limitation of the algorithm. In this
  work, we propose a ground-to-aerial geo-calibration method that can
  further refine the prediction results and estimate the
  camera geo-orientation with overhead imagery.
  %
  We designed a network that can jointly learn the semantic layout of
  the aerial image and its projection to the ground-level perspective.
  When computing the value of constraint function, feed the aerial
  image of a given location and orientation set to the network. 
  By comparing the aerial-to-ground layout with the real layout of the
  ground image, we are able to measure the consistency of these two as
  the value of our constraint function.
  We present the algorithm details in \chapref{crosstransf}.
  \newline
